Contention Management for 5G

### 2017-05-18 article/article.tex
nouvel algo FPT

      Since the exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation. We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failure because of lack of time.

@@

      When the period is less than $40000$, the exhaustive search find much more solutions than the greedy algorithms which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small period, we see that there are very few instances
      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be to restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.

@@

      First, we imagined that prioritise the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:

@@

>>>>

      Since the exhaustive search can fail because there are no solutions or because it does not have enough time to finish its calculation. We represent both the success rate of the algorithm, and an upper bound on the success rate of any algorithm solving PAZL by combining its successes and its failures because of lack of time.

@@

      When the period is less than $40000$, the exhaustive search find many more solutions than the greedy algorithm which justifies its use. 
      However for small period, less than $30000$ the computation time is really important and without improvement it would not be possible to tackle 
      larger problems with $10$ to $20$ routes. Moreover, examining the upper bound curve for small periods, we see that there are very few instances
      with a solution for PAZL. It means that with long routes and high load, looking for an affectation without waiting may be too restrictive.
      That is why we present algorithms for the general PALL problem in our next section. We will test them on $8$ long routes and a period between 
      $20000$ and $30000$ where, as we have shown here, there are often no easy to compute affectation without waiting time.

@@

      First, we imagined that prioritize the messages one the longest route could be a good idea. Thus, the following heuristic is suggested:

@@

     \subsubsection{A fixed parameter tractable solution}

     In this part we try to give a fixed parameter tractable algorithm to solve the PALL problem with parameter $n$ the number of routes.
     This is justified since $n$ is always very small (less than $20$) while $P$, or $\tau$ may be very large.

     \begin{theorem}
      There is an algorithm which solves PALL on star topologies in $O( )$.
     \end{theorem}
     \begin{proof}
      In this algorithm we will guess a certain number of values related to an affectation and then compute in polynomial time
      an affectation which satisfies these properties if it exists. Then the FPT algorithm will be to try every possible set of values 
      and use the polynomial time algorithm.

      We assume we are given the order at which the messages goes through the forward
      period and the order at which the messages goes through the backward period. 
      This is represented by the permutation $\sigma_f$ and $\sigma_b$. \todo{Des notations pour 
      le début des routes dans la backward et la forward}.

      Supposition sans perte de généralité : il n'y a pas de temps d'attente  pour le premier paquet qui passe dans 
      la backward windows.
      Fait: les paquets passent dans la backward windows à un temps au plus 2P plus grand que le premier paquet (peut-être 3P avec
      le temps d'attente). 
      On devine si ils sont entre $O$ et $P$, entre $P$ et $2P$.

      On écrit un système linéaire très simple pour les contraintes de non collision et d'être dans la fenêtre
      et ne pas dépasset $T_{max}$.
      On montre qu'on peut toujours trouver une solution entière à ce système si on a une solution réelle (en tronquant).

      Alternative: donner un algo plus efficace pour trouver la solution qu'un système linéaire avec de la prog dyn.
